### 2020-04-19 final_report/methodology.tex
add section on metrics

>>>>

\subsection{Metrics}
\label{sec:metrics}

Aiming to provide objective comparison of a diverse set of surrogate model
classes, we define a multitude of metrics to be tracked during experiments.
Following the motivation of this work, we are primarily interested in two
properties of surrogates: (i) their capability to approximate the expensive
model well and (ii) their time of evaluation. We strive to maximise the former
while minimising the latter.

To prevent undesirable bias in results due to training set selection, both
properties are collected using $k$-fold cross-validation with a standard choice
of $k=5$. Herein, a sample set is subdivided into 5 disjoint
folds which are repeatedly interpreted as training and testing sets, maintaining
a constant ratio of samples. In each such interpretation experiments are
repeated, and the overall value of each metric of interest is given by the mean
across all folds.

The remainder of this section provides exhaustive list and description of
regression performance and evaluation time metrics recorded in the experiments.

\subsubsection{Regression Performance Metrics}
\label{sec:perf-metrics}

TODO: provide formal definition of each of the following metrics

\begin{description}
	\item[Mean absolute error]
	\item[$R^2$ ratio]
	\item[Adjusted $R^2$ ratio]
	\item[Standard error of regression]
\end{description}

\subsubsection{Evaluation Time Metrics}
\label{sec:time-metrics}

TODO: provide formal definition of each of the following metrics

\begin{description}
	\item[Training time per sample]
	\item[Prediction time per sample]
\end{description}
